### 2018-12-27 tpds/tex/impl.tex
mkdir tpds

% {\color{red}
% \subsection{Cost of adapting DAG frameworks}
% SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}. The concise design makes it easy to adapt DAG frameworks to enable SCache optimization. For example, it only takes about 500 lines of code in Spark to integrate SCache. By a glance of Hadoop source code, we believe that the costs of enabling SCache on MapReduce \cite{hadoop} and YARN \cite{yarn} based DAG computing framework, such as Tez \cite{tez}, are also very low.
% }
{\color{black}
\subsection{Analysis of cross-framework capability}\label{crossframework}
Shuffle optimization of SCache inevitably requires modification on DAG frameworks. SCache provides APIs through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}. In order to use SCache, we mainly need to modify two parts of the frameworks: (a) We need to modify codes in the DAG scheduler to let framework provide DAG information and follow the pre-scheduled result of SCache. (b) The shuffle data between the map task and the reduce task should be transferred to SCahce Storge Management.

To prove the cross-framework capability of SCache, we adapt SCache on Hadoop MapReduce and Spark respectively. Taking Hadoop MapReduce as an example, we modify codes in ResourceManager, MapTask and ReduceTask to call SCache APIs through RPC. It takes about 400 lines of code. In Spark, we mainly modify DAGScheduler and the corresponding data fetcher. 
It only takes about 500 lines of code. Such hundreds of lines of code modification are very small compared to the hundreds of thousands of lines of code in DAG framework. We believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also very low.
}

>>>>

% {\color{red}
% \subsection{Cost of adapting DAG frameworks}
% SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}. The concise design makes it easy to adapt DAG frameworks to enable SCache optimization. For example, it only takes about 500 lines of code in Spark to integrate SCache. By a glance of Hadoop source code, we believe that the costs of enabling SCache on MapReduce \cite{hadoop} and YARN \cite{yarn} based DAG computing framework, such as Tez \cite{tez}, are also very low.
% }
{\color{black}
\subsection{Analysis of cross-framework capability}\label{crossframework}
Shuffle optimization of SCache inevitably requires the modification on DAG frameworks. SCache provides APIs through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}. In order to use SCache, we mainly need to modify two parts of the frameworks: (a) We need to modify codes in the DAG scheduler to let framework provide DAG information and follow the pre-scheduled result of SCache; (b) The shuffle data between the map task and the reduce task should be transferred to SCache Storage Management.

To prove the cross-framework capability of SCache, we adapt SCache on Hadoop MapReduce and Spark respectively. Taking Hadoop MapReduce as an example, we modify codes in ResourceManager, MapTask, and ReduceTask to call SCache APIs through RPC. It takes about 400 lines of code. In Spark, we mainly modify DAGScheduler and the corresponding data fetcher. 
It only takes about 500 lines of code. Such hundreds of lines of code modification are very small compared to the hundreds of thousands of lines of code in DAG framework. We believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also very low.
}
